\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-09-30 sections/methods.tex
Update on Overleaf.

  \subsection*{Consensus network and p-value merging}
  The consensus methods combine networks inferred from both correlation-based and direct association methods.
  \todo[noline]{R1.1}
  \todo[noline]{R1.4}
  \todo[noline]{R2.2}
  \todo[noline]{R2.3}
  First, for the correlation-based methods, we calculate p-values using null models and then merge the p-values using Brown's p-value merging method~\cite{Poole_Gibbs_Shmulevich_Bernard_Knijnenburg_2016,faustCoNetAppInference2016} (see Methods).
  Second, we filter all the inferred networks based on an association strength threshold of 0.1 and a p-value cutoff of 0.05.
  Finally, we apply the consensus algorithms we have developed on these filtered networks.
  These steps are elaborated on in the subsequent sections.

>>>>

  \subsection*{Consensus network and p-value merging}
  The consensus methods combine networks inferred from both correlation-based and direct association methods.
  \todo[noline]{R1.1}
  \todo[noline]{R1.4}
  First, for the correlation-based methods, we calculate p-values using null models and then merge the p-values using Brown's p-value merging method~\cite{Poole_Gibbs_Shmulevich_Bernard_Knijnenburg_2016,faustCoNetAppInference2016}.
  \todo[noline]{R2.2}
  \todo[noline]{R2.3}
  Second, we filter all the inferred networks based on an association strength threshold of 0.1 and a p-value cutoff of 0.05.
  Finally, we apply the consensus algorithms we have developed on these filtered networks.
  These steps are elaborated on in the subsequent sections.
